---
title: "Exploring attribute and spatial data with dplyr and sf"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(dplyr)
library(ggplot2)
gradethis_setup()
theme_set(theme_minimal())

knitr::opts_chunk$set(
  echo = TRUE
  )
```

## Getting started

For this exercise, we are going to start by working with the `storms` data from the {dplyr} package. Use `summary()` to get a quick overview of the `storms` data:

```{r summary, exercise=TRUE}
storms
```

We need to convert `storms` from a data frame into a sf object to visualize and explore spatial dimensions. Using column names for longitude and latitude from the summary, fill in the missing coords parameter for `sf::st_as_sf()`:

```{r st_as_sf, exercise=TRUE}
storms_sf <-
  sf::st_as_sf(
    storms,
    coords = ____
  )

class(storms_sf)
```

```{r st_as_sf-hint}
coords = c("long", "lat")
```

```{r st_as_sf-check}
grade_result(
  pass_if(~ any(grepl(.result, "sf")), "Good job!")
)
```

Following the example of the chapter on [Exploratory Data Analysis](https://r4ds.had.co.nz/exploratory-data-analysis.html) in _R for Data Science_, we are going to start by asking questions about our data. Here are the two kinds of questions we can try:

1. What type of variation occurs within our variables?
2.  What type of covariation occurs between our variables?

You can ask this type of question for any tabular data. When you are working with spatial data, any *variation* may also be spatial variation.

## Exploring variation within variables

You can use a number of different functions from ggplot2, dplyr, and other packages can help explore variation within categorical variables.

### Using `geom_bar()` for categorical variables

`geom_bar()` requires a x or y aesthetic mapping and, by default, counts the number of occurrences for each unique value.

```{r geom_bar_example}
ggplot(data = storms) +
  geom_bar(aes(y = status))
```

### Using `geom_histogram()` for numeric variables

```{r geom_histogram_example}
ggplot(data = storms) +
  geom_histogram(aes(x = wind))
```

### Using `count()` for categorical variables

The `count()` function is a rough equivalent of `df %>% group_by(a, b) %>% summarise(n = n())` with a few additional features. For example, you can set `sort = TRUE` to sort by number of occurences in descending order:

```{r count_example}
count(storms, status, sort = TRUE)
```

The `janitor::tabyl()` provides a similar functionality but generates a formatted table in a rendered RMarkdown or Quarto document. 

```{r tabyl_example}
janitor::tabyl(storms, status)
```

## Explore variation between variables

### Using `geom_boxplot()` and `geom_point()` for contiuous variables

```{r}
#| label: geom_boxplot_example
ggplot(data = storms) +
  geom_boxplot(aes(x = status, y = wind))
```

```{r}
#| label: geom_point_example
ggplot(data = storms) +
  geom_point(aes(x = wind, y = pressure), alpha = 0.1)
```

### Using `janitor::tabyl()` with multiple variables

```{r}
janitor::tabyl(storms, category, status)
```
