---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spatialdatalearnr

<!-- badges: start -->
<!-- badges: end -->

The goal of spatialdatalearnr is to provide interactive tutorials, templates, and other materials to support people participating in the Building Spatial Datasets course at the University of Maryland Baltimore County (UMBC). Learn more [on the course website](https://elipousson.github.io/bldgspatialdata).

## Installation

You can install the development version of spatialdatalearnr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
pak::pkg_install("elipousson/spatialdatalearnr")
```

## Example

```{r}
library(spatialdatalearnr)
```

Once the package is installed you can list available tutorials or run tutorials.

```{r}
available_spatialdata_tutorials()
```

```{r cars, eval=FALSE}
run_spatialdata_tutorial("summarise_sf")
```
